A Standardized Effect Size for Evaluating the Strength of Phylogenetic Signal, and Why Lambda is not Appropriate

### 2020-05-01 Manuscript/SupportingInfo-EKB.Rmd
Supporting figures mostly finished, supporting information markdown started.

**FOR DCA**

1: balanced/symmetric trees
2: Kappa and K_Z
3: Beta from PGLS

@@

*Results*. As found with pure-birth phylogenies, estimates of $\lambda$ varied ..... ** FINISH THIS** (Fig. S1, S2).

```{r, echo = FALSE, out.width="95%"}
include_graphics("Fig1.png")

@@

```{r, echo = FALSE, out.width="95%"}
include_graphics("Fig1.png")

@@

## Literature Survey

>>>>

@@

*Results*. As found with pure-birth phylogenies, estimates of $\lambda$ varied most dramatically in simulations with fewer species and at intermediate values of lambda (Fig. S1, S2). Pectinate trees showed an interesting tendency to underestimate $/lambda$ as 0 for input $/lambda$ values. Most dramatically, some simulations on the largest pectinate phylogeny ($n = 1024$) estimated $/lambda = 0$ for input values as high as 0.75 (Fig. S2).

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS1.png")

@@

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS2.png")

@@

## Simulations of phylogenetic regression and ANOVA

We analyzed the reliability of parameter estimations when used in phylogenetic regression and ANOVA. This involved simulations of dependent variables with $\lambda$ values ranging from 0 to 1 (21 intervals of 0.05 units) across pure-birth trees ($n=2^5 - 2^{10}$). For each $\lambda$ input value, independent variables were then generated with a known relationship ($\beta = 0, 0.25, 0.5, 0.75, 1.0$), from which $\lambda$ was then estimated.

*Results* As with the results from the regression analyses in the main text, we found limmited $\lambda$ estimation precision in smaller trees and at intermediate levels of phylogenetic signal with phylogenetic ANOVA (Fig. S3). Slope was reliably estimated across tree sizes and known $\lambda$ values (Fig. S4).

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS3.png")

\textbf{Figure S3}. Precision of Pagel's $\lambda$ when incorporated in phylogenetic ANOVA. Results are from input $\beta$ values of $0.5$. \hfill\break

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS4.png")

\textbf{Figure S4}. Precision of slope estimates across known input $\beta$ values of phylogenetic regression. Results shown include all input $\lambda$ values. \hfill\break
